---
title: "R programming"
author: "me"
date: "05/01/2021"
output:
  html_document: default
  pdf_document: default
---

## Run RMarkdown on PDF format

We have to download de Texlive program

## Class 1 - video: Writing code/setting your working directory


```{r}
getwd()
```

Exercise: 6
 x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)
 
```{r}
x = c(1,3,5)
y= c(3,2,10)

rbind(x,y)
```
 
 Exercise 8.

Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[1]] give me? Select all that apply.
```{r}
 x <- list(2, "a", "b", TRUE)
 x[[1]]

```

Exercise 9: 
Suppose I have a vector x <- 1:4 and y <- 2:3. What is produced by the expression x + y?

```{r}
x <- 1:4
y <- 2:3.
x+y
```


Exercise 10
Suppose I have a vector x <- c(3, 5, 1, 10, 12, 6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this? Select all that apply.

```{r}
x <- c(3, 5, 1, 10, 12, 6) 


# x[x < 6] == 0 funãço lógica
x[x < 6] <- 0
x[x <= 5] <- 0
x[x %in% 1:5] <- 0
x
```
### Importando os dados
```{r}
hw1_data <- read.csv("~/Documentos/datasciencecoursera/hw1_data.csv")

#print the first two lines of data

head(hw1_data, n=2)

#print the last two lines of data
tail(hw1_data, n=2)

#print ozone in 47th row
print(hw1_data$Ozone[[47]]) 

# missing values ozone variable
test =is.na(hw1_data$Ozone) 

a.test = complete.cases(hw1_data$Ozone)   ## remove NA da variável Ozone
c = hw1_data[a.test,]
mean = mean(c$Ozone)

#What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as NA) from this calculation.
## Easy way
mean(dataset[, "Ozone"], na.rm = TRUE)


miss <- is.na(dataset[, "Ozone"])  ## A vector of TRUE/FALSE
sum(miss)

x = subset(hw1_data, Ozone>31 & Temp>90)
mean(x$Solar.R)

y=subset(hw1_data, hw1_data$Month==6)
mean(y$Temp)

z = subset(hw1_data, hw1_data$Month==5)
z1=na.omit(z)
max(z1$Ozone)
```


### Subsetting nested elements of a list

```{r}
k = list(a=list(10,11,12), b=c(3.14, 2.81))

# resultados equivalentes
k[[c(1, 3)]]  #no elemento 1, print elem 3
k[[1]][[3]]
k[[c(2,1)]]

```



